Towards Explainability of Machine Learning Models in Insurance Pricing

### 2019-10-26 manuscript/manuscript.Rmd

As noted earlier, the ordering of variables has an impact on the contributions calculated, especially for models that are non-additive, which could cause inconsistent explanations. There are several approaches to ameliorate this phenomenon, including selecting variables with the largest contributions first, including interactions terms, and averaging over possible orderings; these are discussed further in @biecekPMVEE and its references.

@@

(TODO: briefly discuss other stuff not covered)

>>>>

As noted earlier, the ordering of variables has an impact on the contributions calculated, especially for models that are non-additive, which could cause inconsistent explanations. There are several approaches to ameliorate this phenomenon, including selecting variables with the largest contributions first, including interactions terms, and averaging over possible orderings. The last of these ideas is implemented by @NIPS2017_7062 using Shapley values from cooperative game theory, and is referred to as Shapley additive explanations (SHAP). These approaches are discussed further in @biecekPMVEE and its references.

@@

In this paper, we demonstrate just a few model-agnostic ML interpretation techniques. These represent a small subset of existing techniques, each of which have additional variations. In the remainder of this section, we point out a few common techniques not covered in our case study.

Individual conditional expectation (ICE) plots disaggregate PDPs into their instance-level components for a more granular view into predictor sensitivities [@goldstein2015peeking]. To accommodate correlated variables in PDP, accumulated local effect (ALE) plots computes expected changes in model response over the conditional, rather than marginal, distribution of the other variables [@apley2016visualizing].

Local interpretable model-agnostic explanations (LIME) [@ribeiro2016should] builds simple surrogate models using model predictions, with higher training weights given to the point of interest, in effect replacing the complex ML model with an easily interpretable linear regressions or decision trees in neighborhoods of specific points for the purpose of explanation. Taking the concept further, one can also train a global surrogate model across the entire domain of interest.
